\documentclass{surv-l}


\begin{document}

\begin{center}
1980  \emph{Mathematics Subject Classification} (1985 \emph{Revision}). Primary 34B25,
\end{center}
35P25, 58F07.


\centerline{\rule{10pc}{0.5pt}}


\section*{Library of Congress Cataloging-in-Publication Data}


\noindent Beals, Richard, 1938-

Direct and inverse scattering on the line/Richard Beals, Percy Deift, and Carlos Tomei.

p. cm. - (Mathematical surveys and monographs)

Bibliography: p.

ISBN 0-8218-1530-X (alk. paper)

1. Scattering (Mathematics) 2. Inverse scattering transform. I. Deift, Percy, 1945-.
II. Tomei, Carlos. III. Title. IV. Series.

QA329.B43\quad1988

515.7$'$24 -- dc19\hphantom{12}\hfill 88-14487\\

\hfill CIP

\centerline{\rule{10pc}{0.5pt}}


\section*{Copying and reprinting} 

Individual readers of this publication, and nonprofit libraries acting for them, are permitted to make fair use of the material, such as to copy a chapter for use in teaching or research. Permission is granted to quote brief passages from this publication in reviews, provided the customary acknowledgment of the source is given.

Republication, systematic copying, or multiple reproduction of any material in this publication (including abstracts) is permitted only under license from the American Mathematical Society. Requests for such permission should be addressed to the Executive Director, American Mathematical Society, P.O. Box 6248, Providence, Rhode Island 02940.

The owner consents to copying beyond that permitted by Sections 107 or 108 of the U.S. Copyright Law, provided that a fee of {\$}1.00 plus {\$}.25 per page for each copy be paid directly to the Copyright Clearance Center, Inc., 21 Congress Street, Salem, Massachusetts 01970. When paying this fee please use the code 0076-5376/88 to refer to this publication. This consent does not extend to other kinds of copying, such as copying for general distribution, for advertising or promotion purposes, for creating new collective works, or for resale.

\begin{center}
Copyright \copyright 1988 by the American Mathematical Society. All rights reserved. Printed in the United States of America

The American Mathematical Society retains all rights

except those granted to the United States Government.


The paper used in this book is acid-free and falls within the guidelines

established to ensure permanence and durability. \circledinfty
\end{center}

\end{document} 