\begin{copyrightpage}
\begin{center}
\textbf{Editorial Board}\\
Georgia M. Benkart \qquad  Tudor Stefan Ratiu, Chair\\
Peter Landweber \qquad\quad\ Michael Renardy
\end{center}

\begin{center}
1991 \emph{Mathematics Subject Classification}. Primary 60H15;
Secondary 35R60.
\end{center}

\noindent \textsc{Abstract.} Stochastic Partial Differential
Equations is an interdisciplinary area on the crossroads of
stochastic processes (random fields) and partial differential
equations. This volume presents the topic of SPDE's from different
perspectives, as seen by six groups of researchers working in the
most active and promising areas of the field. The goal of this book
is to indicate what the main topics of interest are in this
fascinating field, and where breakthroughs are being made today.

This book will be of interest to graduate students and researchers in various areas of Mathematics, Physics, Engineering, Economics, etc.\\

\hrulefill\\

\noindent \textbf{Library of Congress Cataloging-in-Publication
Data}

\noindent Stochastic partial differential equations : six
perspectives / Rene A. Carmona, Boris Rozovskii, editors.

\quad p.cm. --- (Mathematical surveys and monographs, ISSN 0076-5376
; v. 64)

Includes bibliographical references (p. - )and index.

ISBN 0-8218-0806-0 (alk. paper)

1. Stochastic partial differential equations. I. Carmona, R.
(Ren\'{e}) II. Rozovski\u{\i}, B. L. (Boris L$^{\prime}$vovich) III.
Series: Mathematical surveys and monographs ; no. 64.

\noindent QA274.25.S746 \quad  1998

\noindent 519.2---dc2l \hfill 98-38392

\hfill CIP\\

\hrulefill\\

\noindent \textbf{Copying and reprinting.} Material in this book may
be reproduced by any means for educational and scientific purposes
without fee or permission with the exception of reproduction by
services that collect fees for delivery of documents and provided
that the customary acknowledgment of the source is given. This
consent does not extend to other kinds of copying for general
distribution, for advertising or promotional purposes, or for
resale. Requests for permission for commercial use of material
should be addressed to the Assistant to the Publisher, American
Mathematical Society, P. O. Box 6248, Providence, Rhode Island
02940-6248. Requests can also be made by e-mail to
\textbf{\texttt{reprint-permission@ams.org}}.

Excluded from these provisions is material in articles for which the
author holds copyright. In such cases, requests for permission to
use or reprint should be addressed directly to the author(s).
(Copyright ownership is indicated in the notice in the lower
right-hand corner of the first page of each article.)

\begin{center}
$\copyright$ 1999 by the American Mathematical Society. All rights reserved.\\
The American Mathematical Society retains all rights\\
except those granted to the United States Government.\\
Printed in the United States of America.
\end{center}

\begin{center}
$\circledinfty$\ The paper used in this book is acid-free and falls within the guidelines\\
established to ensure permanence and durability.\\
Visit the AMS home page at \textbf{URL:
\texttt{http://www.ams.org/}}
\end{center}

\begin{center}
10 9 8 7 6 5 4 3 2 \qquad 04 03 02 01 00 99
\end{center}
\end{copyrightpage}
