\begin{copyrightpage}
\begin{center}
\textbf{Editorial Board}

\begin{tabular}{lllll}
Georgia Benkart & & & & \quad Michael Loss\\
Peter Landweber & & & & \quad Tudor Ratiu, Chair\\
\end{tabular}
\end{center}

\begin{center}
2000 \textit{Mathematics Subject Classification}. Primary 46L54;
Secondary 15A52, 60F10, 94A17, 46N50, 60J65, 81S25, 05A17.
\end{center}

\noindent \textsc{abstract}. This is an expository monograph on free
probability theory. The emphasis is put on entropy and random matrix
models. The highlight is the very far-reaching interrelation of free
probability and random matrix theories. Wigner's theorem and its
broad generalizations, such as asymptotic freeness of independent
matrices, are expounded in detail. The parallelism between the
normal and semicircle laws runs through the book. Many examples are
included to illustrate the results. The frequent random matrix
ensembles are characterized by maximization of their Boltzmann-Gibbs
entropy under certain constraints, and the asymptotic eigenvalue
distribution is treated in the almost everywhere sense and in the
form of large deviation. Voiculescu's multivariate free entropy is
presented with full proofs and extended to unitary operators. Some
ideas about applications to operator algebras are also given.

\hrulefill\\

\noindent \textbf{Library of Congress Cataloging-in-Publication
Data}

\noindent Hiai, Fumio, 1948--

\quad The semicircle law, free random variables, and entropy / Fumio
Hiai, D\'{e}nes Petz.

\qquad p. cm. --- (Mathematical surveys and monographs, ISSN
0076-5376 ; v. 77)

\quad Includes bibliographical references and index.

\quad ISBN 0-8218-2081-8 (alk. paper) \quad ISBN 0-8218-4135-1
(softcover)

\quad 1. Free probability theory. 2. Random matrices. 3. Entropy. I.
Petz, D\'{e}nes, 1953--

II. Mathematical surveys and monographs\, ; no. 77.

QA326 .H52 \quad 2000

512$'$.55--dc21 \hfill 99-088288

\hrulefill\\

\textbf{Copying and reprinting.} Individual readers of this
publication, and nonprofit libraries acting for them, are permitted
to make fair use of the material, such as to copy a chapter for use
in teaching or research. Permission is granted to quote brief
passages from this publication in reviews, provided the customary
acknowledgment of the source is given.

Republication, systematic copying, or multiple reproduction of any
material in this publication is permitted only under license from
the American Mathematical Society. Requests for such permission
should be addressed to the Acquisitions Department, American
Mathematical Society, 201 Charles Street, Providence, Rhode Island
02904-2294, USA. Requests can also be made by e-mail to
\texttt{reprint-permission@ams.org.}

\begin{center}
\textcopyright\ 2000 by the American Mathematical Society. All
rights reserved.\\
The American Mathematical Society retains all rights\\
except those granted to the United States Government.\\
Printed in the United States of America.

\circledinfty\ The paper used in this book is acid-free and falls
within the guidelines\\
established to ensure permanence and durability.\\
Visit the AMS home page at \texttt{http://www.ams.org/}

10 9 8 7 6 5 4 3 \qquad 11 10 09 08
\end{center}
\end{copyrightpage}
